The problem and promise of scale in multilayer animal social networks

### 2020-02-14 paper/manuscript.Rmd
little mov perspective edits

Social processes, movement decisions, and space use are inextricably linked and
multilayer networks represent a potential analytical framework for linking these
processes [@Mourier_2019] (Mourier et al. 2019). Movement as a collective group
can reduce per capita predation risk via detection-dilution trade-offs and
improve information transfer about the quality or location of resources to other
group members [@Jolles_2019]. In our case study, we integrate proximity based
social networks that inherently rely on animal collective movement and, in
general, we found that movement is likely an important mechanism driving social
network connectivity within and between habitat types.

Although multilayer animal social networks are relatively novel [@Silk_2018],
movement behaviour within multilayer networks has been considered.  Spatial
networks are physical locations (nodes) which are connected in a network when
individuals move between said locations (edges). For example, spatial networks
were applied to monitor movement of sharks (*Carcharhinus amblyrhynchos* and
*Carcharhinus melanopterus*) between fixed location autonomous arrays. In this
example, nodes represent locations within the array, *intralayer edges*
represent individual movement frequency, and *interlayer edges* represent
contact probability among individuals at a given node [@Mourier_2019] (Mourier
et al. 2019). Although movement between fixed arrays is inherent, networks are
not constructed based on continuous measures of dyadic or collective movement
[@Long_2014]. Our case study builds on the work of Mourier et al. (2019) and
explicitly integrates continuous and simultaneous measures of animal movement
through space and time as layers of a multilayer social network.

@@

Given the existing framework for constructing multilayer networks from
behavioural layers [e.g. @Smith_Aguilar_2019], monolayer networks that explicity
quantify movement paramters could be itnegrated. For example, edges could
represent measures of dyadic or collective movement based on dynamic interaction
metrics [@Long_2014]. Integrating movement layers with habitat-specific social
association layers could further shed light on the role of movement as a driver
of the social and spatial environments an individual experiences [@Webber_2018].
In our case study, we generated multilayer networks based on habitat-specific
monolayers. Coordinated movement of dyads, or groups, could vary based on
habitat, and the approach we outline could be used to explore mechanisms linking
the social and spatial environments. For example, social processes may be an
emergent property of the landscape because animals aggregate at resources, such
as waterholes [@Chamaillé_Jammes_2008]. Movement to, from, or within habitat
patches  or territories can also contribute to the formation of the social
environment [@Spiegel_2016]. For example, in sleepy lizards (*Tiliqua rugosa*)
males interacted primarily at home range edges, presumably driving territorial
behaviour [@Spiegel_2018]. Incorporating movement ecology within a multilayer
network framework is a logical next step for a burgeoning field. In particular,
when association networks are habitat-specific, we suggest the integration of
movement and space use in multilayer networks provides novel insights into the
effects of habitat configuration on the formation of the social environment
[@He_2019].

>>>>

Social processes, movement decisions, and space use are inextricably linked and
multilayer networks represent a potential analytical framework for linking these
processes [@Mourier_2019]. Movement as a collective group
can reduce per capita predation risk via detection-dilution trade-offs and
improve information transfer about the quality or location of resources to other
group members [@Jolles_2019]. In our case study, we integrate proximity based
social networks that inherently rely on animal collective movement and, in
general, we found that movement is likely an important mechanism driving social
network connectivity within and between habitat types.

Although multilayer animal social networks are relatively novel [@Silk_2018],
movement behaviour within multilayer networks has been considered.  Spatial
networks are physical locations (nodes) which are connected in a network when
individuals move between said locations (edges). For example, spatial networks
were applied to monitor movement of sharks (*Carcharhinus amblyrhynchos* and
*Carcharhinus melanopterus*) between fixed location autonomous arrays. In this
example, nodes represent locations within the array, *intralayer edges*
represent individual movement frequency, and *interlayer edges* represent
contact probability among individuals at a given node [@Mourier_2019]. Although movement between fixed arrays is inherent, networks are
not constructed based on continuous measures of dyadic or collective movement
[@Long_2014]. Our case study builds on the work of Mourier et al. (2019) and
explicitly integrates continuous and simultaneous measures of animal movement
through space and time as layers of a multilayer social network.

@@

Given the existing framework for constructing multilayer networks from
behavioural layers [e.g. @Smith_Aguilar_2019], monolayer networks that explicity
quantify movement paramters could be itnegrated. For example, edges could
represent measures of dyadic or collective movement based on dynamic interaction
metrics [@Long_2014]. Integrating movement layers with habitat-specific social
association layers could further illuminate the role of movement as a driver
of the social and spatial environments an individual experiences [@Webber_2018].
In our case study, we generated multilayer networks based on habitat-specific
monolayers. Coordinated movement of dyads, or groups, could vary based on
habitat, and the approach we outline could be used to explore mechanisms linking
the social and spatial environments. For example, social processes may be an
emergent property of the landscape because animals aggregate at resources, such
as waterholes [@Chamaillé_Jammes_2008]. Movement to, from, or within habitat
patches  or territories can also contribute to the formation of the social
environment [@Spiegel_2016]. For example, in sleepy lizards (*Tiliqua rugosa*)
males interacted primarily at home range edges, presumably driving territorial
behaviour [@Spiegel_2018]. Incorporating movement ecology within a multilayer
network framework is a logical next step for a burgeoning field. In particular,
when association networks are habitat-specific, we suggest the integration of
movement and space use in multilayer networks provides novel insights into the
effects of habitat configuration on the formation of the social environment
[@He_2019; @Webber_2018].
